

\chapter{Budget} \label{chap:budget}
% \vspace*{-0.3cm}
%% recuerda mover este capitulo que sea el de antes de las conclusiones en el mismo formato que los otros

Before presenting our conclusions to this work, we include an estimate of the costs associated with the realization of this work in an attempt to provide a more complete picture of the project.

\section{Cost of Human Resources}

We start with the costs of human resources associated, the student author of the work and the advisor and co-advisor of the thesis are considered to be the main contributors to the project. The student author is considered to have worked on the project in a part-time to full-time basis for the duration of the work, while the advisor and co-advisor contributed a few hours per week. 

The salary per hour of each contributor was estimated to be €18, €30, and €60, respectively, to reflect the estimated salaries of a junior researcher, senior researcher, and university professor.

By analyzing the time planning of the project throughout its duration \todo{include Gannt chart?}, the project is estimated to have lasted approximately eight months. During this time, the author contributed an estimated total of 530 hours, while the advisor and co-advisor an estimate of 25 and 35 hours, respectively. 

Table \ref{tab:budget-human_resources} shows a summary of the estimated costs of human resources, giving a \textbf{total budget of €13140.00} associated with the labor costs of this work.

\begin{table}[h]
    \centering
    % \captionsetup[]{}
    \caption{Estimated Costs of Human Resources}
    \label{tab:budget-human_resources}
    % \hspace*{-0.8cm}
    \begin{tabular}{lrrr}
    \toprule
    {} &  \# of Hours &  Salary per hour (€) &  Total Salary (€) \\
    \midrule
    Author  &                   530 &                   18 &         9540 \\
    Co-Advisor &                35 &                    30 &         1050 \\
    Advisor &                   25 &                    60 &         1500 \\
    \bottomrule
    {} &  {} & \textbf{Total Cost:} & \textbf{€12090.00} \\
    \end{tabular}
\end{table}

% \vspace{-0.4cm}

\section{Software/Cloud Expenses and Material Costs}

In terms of non-human resource costs, the main relevant ones are those associated with the material costs utilized throughout the work. This is because we mainly used open-source software tools (Python, LaTeX, PyTorch etc.) in our work. These tools are freely available or under permissive licenses. Thus, no costs are associated with them.

Google Colab was the only tool used that is not open-source. Because of the demanding nature of some of the experiments we tried with, we bought a total of 10\$ worth of Google Cloud credits to use the service. This is the only cost associated with \textbf{software and licenses} in this work.

In terms of material costs, we consider the following:

\begin{itemize}
    \item The personal computer from which the thesis was written and experiments designed and executed. The device consisted of a 14" Apple Macbook Pro (2021) valued at €2200 at the time of writing \cite{apple_comprar_2022}. With a 3-year depreciation of €733.33 divided by the duration of the project, this would add €489 to the material costs associated with this work.
    \item Other equipment, lab materials (e.g., paper, pens, etc.), and other miscellaneous costs are considered negligible and are not included in the budget.
\end{itemize}

% Table \ref{tab:budget-material_costs} shows a summary of the material costs associated with this project:

\begin{table}[H]
    \centering
    \captionsetup[]{}
    \caption{Estimated Material Costs}
    \label{tab:budget-material_costs}
    % \hspace*{-0.8cm}
    \begin{tabular}{lrrrr}
    \toprule
    {} &  Software \& Licenses &  Personal Computer & Miscellaneous  & \textbf{Total} \\
    \midrule
    Cost (€)  &  10 & 489 &  0 & \textbf{€499} \\
    \end{tabular}
\end{table}
% \vspace*{-0.4cm}

Thus, the total material costs associated with this work are estimated to be €499.00. If we add that to the cost of human resources, we can calculate a \textbf{total budget of €12,579.00} associated with its realization.